---
title: "Course8Project"
output: html_document
---

##Data Reading

```{r}
rawdata<-read.csv("pml-training.csv", na.strings=c("NA", ""))
set.seed(33)
```

##Data Cleaning
* Using columns sensor information and classe information
* Only using columns which has more than 19000 values which are not NA

```{r}
sensorColumns = grep(pattern = "_belt|_arm|_dumbbell|_forearm", names(rawdata))
cleandata = rawdata[, c(sensorColumns,160)]
missingData = is.na(cleandata)
omitColumns = which(colSums(missingData) > 19000)
cleandata = cleandata[, -omitColumns]
```

## Data partitioning

Setting 75% of data for training

```{r}
library(randomForest)
library(caret)
library(ggplot2)
inTrain <- createDataPartition(y=cleandata$classe, p=0.75, list=FALSE)
training <- cleandata[inTrain,]
testing <- cleandata[-inTrain,]
```

## Checking data visually

### Checking count of each classe
```{r}
qplot(classe,data=training, col=classe)
```

### Picking random colums to see if data can be seprated based on 2 features
```{r}
qplot(pitch_belt, accel_forearm_y, col=classe, data=training)
qplot(gyros_belt_y, gyros_arm_y, col=classe, data=training)
```

Conclusion: Two features are not enough to seperate data. It was obvious!

## Generating model
Usind randomforest to come up with model
```{r}
randForest = randomForest(classe~., data=training, ntree = 500)
```

## Running prediction

Predicting testing data using randomForest modek and comparing it against classe column using confusion matrix

```{r}
prediction = predict(randForest, newdata = testing)
confusionMatrix(prediction, testing$classe)
```

Accuracy of model on test data is >95%